\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % change the width of the column with the dates

% \renewcommand{\homepage}[2][Homepage]{%
%   \def\@homepagetitle{#1}%
%   \def\@homepage{#2}%
%   \@homepage
% }


% personal data
\name{Wei-Chih}{Huang}
\email{s104021230@tamu.edu}
\homepage{noctildon.github.io}
\social[googlescholar][scholar.google.com/citations?user=3_6lzj4AAAAJ]{huang}
\social[linkedin][www.linkedin.com/in/wei-chih-huang-38b075233]{linkedin}
\social[github][github.com/noctildon]{github}
\social[inspire][inspirehep.net/authors/2661451]{\inspiresocialsymbol inspireHEP}



\begin{document}
\makecvtitle

\section{Education}
\cvitem{Aug. 2019 --}{\textit{PhD in Physics}}
\cvitem{Dec. 2025}{\textbf{Texas A\&M University, US}}
\cvitem{Aug. 2015 --}{\textit{BS in Physics}}
\cvitem{Jun. 2019}{\textbf{National Tsing Hua University, Taiwan}}


\section{Fields of Interest}
\cvitem{}{Dark Matter, High Energy Physics (phenomenology), Nuclear Physics, Nuetrino Physics}

\section{Professional Experience}
\cvitem{Aug. 2019 --}{\textbf{Graudate Research Assistant}}
\cvitem{present}{\textit{Physics \& Astronomy department, Texas A\&M University, US}}
\cvitem{}{$\bullet$ Design and calculate the structure of various kinds of nuclei by FORTRAN, MPI/OpenMP, Python, and Mathematica}
\cvitem{}{$\bullet$ Construct models for dark matter and axion and the interaction with nuclei}
\cvitem{}{$\bullet$ Programmed Python to do data analysis and statistical analysis}
\cvitem{}{}


\cvitem{Nov. 2017 --}{\textbf{Inflation and Late-time Acceleration in $f(R)$ Gravity Theory}}
\cvitem{Jun. 2019}{\textit{Physics department, National Tsing Hua University, Taiwan}}
\cvitem{}{$\bullet$ Formalized the evolution of the universe by $f(R)$ modified gravity}
\cvitem{}{$\bullet$ Programmed Mathematica and Python to stimulate the evolution of the universe}
\cvitem{}{}

\cvitem{Jul. 2018 --}{\textbf{Dark Matter in Merging Galaxies}}
\cvitem{Aug. 2018}{\textit{The University Consortium of ALMA–Taiwan}}
\cvitem{}{$\bullet$ Did data analysis and data visualization on dark matter around Galactic center}
\cvitem{}{$\bullet$ Used CASA to clean, analyze and visualize the data imaging from extragalactic database, and infer the dark matter distribution}
\cvitem{}{$\bullet$ Automated the entire analysis process by Python}


\section{Publications}
\cvitem{}{\textbf{Novel Approach to Investigate ATOMKI Anomaly Using Coherent CAPTAIN-Mills Detectors} \hfill \href{https://inspirehep.net/literature/2781328}{inspireHEP}}
\cvitem{Oct. 2024}{\footnotesize Bhaskar Dutta, Bai-Shan Hu, \textit{\textbf{Wei-Chih Huang}}, Richard G. Van de Water}
\cvitem{}{}
\cvitem{}{\textbf{Indirect detection of dark matter absorption in the Galactic Center} \hfill \href{https://inspirehep.net/literature/2781328}{inspireHEP}}
\cvitem{Apr. 2024}{\footnotesize Kimberly K. Boddy, Bhaskar Dutta, Addy J. Evans, \textit{\textbf{Wei-Chih Huang}}, Stacie Moltner, Louis E. Strigari}
\cvitem{}{}
\cvitem{}{\textbf{Prospects for Light Dark Matter Searches at Large-Volume Neutrino Detectors} \hfill \href{https://inspirehep.net/literature/2756023}{inspireHEP}}
\cvitem{Feb. 2024}{\footnotesize Bhaskar Dutta, \textit{\textbf{Wei-Chih Huang}}, Doojin Kim, Jayden L. Newstead, Jong-Chul Park, Iman Shaukat Ali}
\cvitem{}{}
\cvitem{}{\textbf{Short Baseline Neutrino Anomalies at Stopped Pion Experiments} \hfill \href{https://inspirehep.net/literature/2713130}{inspireHEP}}
\cvitem{Oct. 2023}{\footnotesize Iain A. Bisset, Bhaskar Dutta, \textit{\textbf{Wei-Chih Huang}}, Louis E. Strigari}
\cvitem{}{}
\cvitem{}{\textbf{Probing the dark sector with nuclear transition photons} \hfill \href{https://inspirehep.net/literature/2635065}{inspireHEP}}
\cvitem{Feb. 2023}{\footnotesize Bhaskar Dutta, \textit{\textbf{Wei-Chih Huang}}, Jayden L. Newstead}
\cvitem{}{}
\cvitem{}{\textbf{Inelastic nuclear scattering from neutrinos and dark matter} \hfill \href{https://inspirehep.net/literature/2097598}{inspireHEP}}
\cvitem{Dec. 2022}{\footnotesize Bhaskar Dutta, \textit{\textbf{Wei-Chih Huang}}, Jayden L. Newstead, Vishvas Pandey}
\cvitem{}{}
\cvitem{}{\textbf{Axion-Like Particle Production at Beam Dump Experiments with Distinct Nuclear Excitation Lines} \hfill \href{https://inspirehep.net/literature/2126695}{inspireHEP}}
\cvitem{Aug. 2022}{\footnotesize Loyd Waites, Adrian Thompson, Adriana Bungau, Janet M. Conrad, Bhaskar Dutta, \textit{\textbf{Wei-Chih Huang}}, Doojin Kim, Michael Shaevitz, Joshua Spitz}


\section{Talks}
\cvitem{Apr. 2023}{\href{https://www.int.washington.edu/programs-and-workshops/23-85w}{\textbf{Interplay of Nuclear, Neutrino and BSM Physics at Low-Energies}}}
\cvitem{}{Probing BSM particles using inelastic nuclear scattering}
\cvitem{}{}

\cvitem{Oct. 2022}{\href{https://indico.cern.ch/event/1191939/}{\textbf{Particle Physics on the Plains}}}
\cvitem{}{Inelastic Dark Matter-Nucleus Scattering in Stopped-pion Experiments using Transition Photons}
\cvitem{}{}

\cvitem{May. 2022}{\href{https://indico.cern.ch/event/1089132/}{\textbf{2022 Phenomenology Symposium}}}
\cvitem{}{Inelastic neutrino-nucleus and dark matter-nucleus scattering}
\cvitem{}{}

\cvitem{Jul. 2021}{\href{https://indico.cern.ch/event/1034469}{\textbf{2021 Meeting of the Division of Particles and Fields of the American Physical Society (DPF21)}}}
\cvitem{}{The calculation of inelastic neutrino-nucleus scattering}

\cvitem{}{}
\cvitem{Oct. 2021}{\href{https://indico.cern.ch/event/1075677/}{\textbf{2021 Magnificent CEvNS Workshop}}}
\cvitem{}{Inelastic neutrino-nucleus and dark matter-nucleus scattering}
\cvitem{}{}


\section{Teaching Experience}
\cvitem{2022 --}{\textbf{TAMU Physics Department}}
\cvitem{2023}{Workshop Lecturer: Data Science in Physics \href{https://noctildon.github.io/DS_ambassador/index.html}{(webpage)}}
\cvitem{}{}

\cvitem{Fall 2022}{\textbf{TAMU Physics 207, Electricity and Magnetism for Engineering and Science}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}

\cvitem{Summer}{\textbf{TAMU Physics 207, Electricity and Magnetism for Engineering and Science}}
\cvitem{2022}{Teaching Assistant (Lab)}
\cvitem{}{}

\cvitem{Spring 2022}{\textbf{TAMU Physics 207, Electricity and Magnetism for Engineering and Science}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}

\cvitem{Fall 2021}{\textbf{TAMU Physics 206, Newtonian Mechanics for Engineering and Science}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}

\cvitem{Spring 2021}{\textbf{TAMU Physics 207, Electricity and Magnetism for Engineering and Science}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}

\cvitem{Fall 2020}{\textbf{TAMU Physics 207, Electricity and Magnetism for Engineering and Science}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}

\cvitem{Spring 2020}{\textbf{TAMU Physics 206, Newtonian Mechanics for Engineering and Science}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}

\cvitem{Fall 2019}{\textbf{TAMU Physics 408, Thermodynamics and Statistical Mechanics}}
\cvitem{}{Teaching Assistant (grader)}
\cvitem{}{}

\cvitem{Spring 2016}{\textbf{Shu Guang Girls’ Senior High school}}
\cvitem{}{Teaching Assistant}
\cvitem{}{}


\section{Honors and Awards}
\cvitem{}{\textbf{Data Science Ambassador Scholarship}}
\cvitem{Fall 2022}{Data Science Ambassador Scholarship Program at Texas A\&M Institute of Data Science}
\cvitem{}{}
\cvitem{}{\textbf{Undergraduate Research Scholarship}}
\cvitem{Fall 2018}{Scholarship for the $f(R)$ gravity project}
\cvitem{}{}
\cvitem{}{\textbf{Three Years Tsing Hua University Scholarship (2\% acceptance rate)}}
\cvitem{2015 - 2018}{Tuition wavier, including housing and textbooks}



\section{Programming Skills}
\cvitem{}{Python, NumPy, Pandas, Matplotlib, SciPy, PyTorch, TensorFlow}
\cvitem{}{Bash, Git, GitHub, Docker, Mathematica, Javascript, LaTeX}


\end{document}