% https://www.overleaf.com/latex/templates/cis-grad-template-dev/pjcttwysqvym

% Use the custom resume.cls style
\documentclass{resume}

% Document margins
\usepackage[top=0.15in, bottom=0.15in, right=0.4in, left=0.3in]{geometry}
\usepackage{fontawesome}


\name{Wei-Chih Huang}
\address{
\href{mailto:noctildon2@gmail.com}{\faEnvelope\, noctildon2@gmail.com} \\
\href{https://www.linkedin.com/in/wei-chih-huang}{\faLinkedinSquare \,/in/wei-chih-huang} \\
\href{https://github.com/noctildon}{\faGithub \, noctildon} \\
\href{https://noctildon.github.io}{\faDesktop \, Personal Site}
}


\begin{document}

\vspace{-1.5em}
\begin{rSection}{Education}
\vspace{-0.25em}
{\bf PhD in Physics}, Texas A\&M University, US \hfill {Aug. 2019 - Aug. 2025 (expected)} \\
{\bf BS in Physics}, National Tsing Hua University, Taiwan \hfill {Aug. 2015 - Jun. 2019}
\end{rSection}


% \vspace{-0.5em}
\begin{rSection}{Experience}
    \vspace{-1em}
    \item \textbf{Quantitative Engineer} - Aggie Quant Fund, Texas A\&M University \hfill Jan. 2024 - present
        \begin{itemize}
        \item Construct a high-performance backtesting framework that supports automization and visualization
        \item Developed and tested trading strategies
        \end{itemize}

    \item \textbf{Research Assistant} - Physics Department, Texas A\&M University (\href{https://inspirehep.net/authors/2661451}{researcher profile}) \hfill Aug. 2019 - present
        % \newline\hspace*{0.5em} {\normalsize PhD dissertation topic on dark matter search using nucleus scattering}
        \begin{itemize}
        \item Built physical models and conducted the statistical analysis on the large multi-dimensional data by Python
        \item Automized and visualized the analysis with NumPy, SciPy, Pandas, and Matplotlib to save 90\% of time
        \item Accelerated the analysis by 1000 times with dedicated algorithm, multiprocessing, caching, and C\texttt{++}
        \item Published 6 papers in high impact journals and presented several successful talks at international conferences
        \end{itemize}

    \item \textbf{Independent Data Science Researcher} - {Pro Cyclists Race Analysis} (\href{https://github.com/noctildon/pro_cyclists}{Github repo}) \hfill Apr. 2022 - present
        % \newline\hspace*{0.5em} {\normalsize Data analysis of professional cycling races and forecasted of the outcomes by machine learning models}
        \begin{itemize}
        \item Web scraped a website using BeautifulSoup and increased the performance by 500\% with multi-threading
        \item Preprocessed the data (clean, format, store) with NumPy, Pandas, SciPy, scikit-learn, and PySpark
        \item Construct machine learning models with PyTorch and sciki-learn
        \item Saved 80\% costs compared to AWS, GCP, Azure by deploying data and model to Runpod (GPU cloud)
        \item Achieved 20\% better performance than a trivial model
        \end{itemize}

    \item \textbf{Data Science Ambassador} - Physics Department, Texas A\&M University \hfill Aug. 2022 - Aug. 2023
        % \newline\hspace*{0.5em} {\normalsize Data Science Ambassador representing Physics Department}
        \begin{itemize}
        \item Provided training and consulting to the department and the students (\href{https://noctildon.github.io/DS_ambassador/index.html}{webpage})
        \item Designed interactive workshops on topics including Python, Linux, statistics, data analysis, and machine learning
        \end{itemize}

    \item \textbf{Full-Stack Web Developer/Project Manager} - \href{https://aggiecodingclub.com}{Aggie Coding Club} \hfill Jan. 2022 - Jan. 2023
        % \newline\hspace*{0.5em} {\normalsize A dynamic website designed to cater to students' job-seeking requirements ({\href{https://github.com/noctildon/aggie-job-referral}{github repo}})}
        \begin{itemize}
            \item Led a 10-people team and organized the tasks to the team members
            \item Provided training and mentoring for the team members about Git, GitHub, Python, Linux and database
            \item Developed a dynamic and responsive website using Django (Python) and Bootstrap (HTML, CSS, JavaScript)
            \item Designed PostgreSQL database schema to save the disk space by 20\%
            \item Built a referral machine to reduce the time of networking by 40\%
            \item Deployed the website at zero cost on Heroku cloud platform
        \end{itemize}
\end{rSection}


% \vspace{-0.5em}
\begin{rSection}{Publications}
    \begin{itemize}
        \item Probing the dark sector with nuclear transition photons \hfill \href{https://arxiv.org/pdf/2302.10250.pdf}{arxiv}
        % \newline{\footnotesize \it Bhaskar Dutta, \textbf{Wei-Chih Huang}, Jayden L. Newstead}
        \item Inelastic nuclear scattering from neutrinos and dark matter \hfill \href{https://arxiv.org/pdf/2206.08590.pdf}{arxiv}
        % \newline{\footnotesize \it Bhaskar Dutta, \textbf{Wei-Chih Huang}, Jayden L. Newstead, Vishvas Pandey}
        \item Short Baseline Neutrino Anomalies at Stopped Pion Experiments \hfill \href{https://arxiv.org/abs/2310.13194}{arxiv}
        % \newline{\footnotesize \it Iain A. Bisset, Bhaskar Dutta, \textbf{Wei-Chih Huang}, Louis E. Strigari}
        \item Axion-Like Particle Production at Beam Dump Experiments with Distinct Nuclear Excitation Lines \hfill \href{https://arxiv.org/pdf/2207.13659.pdf}{arxiv}
        % \newline{\footnotesize \it Loyd Waites, Adrian Thompson, Adriana Bungau, Janet M. Conrad, Bhaskar Dutta, \textbf{Wei-Chih Huang}, Doojin Kim, Michael Shaevitz}
        \item Exciting Prospects for Dark Matter at Large-Volume Neutrino Detectors \hfill \href{https://arxiv.org/abs/2402.04184}{arxiv}
        % \newline{\footnotesize \it Bhaskar Dutta, \textbf{Wei-Chih Huang}, Doojin Kim, Jayden L. Newstead, Jong-Chul Park, Iman Shaukat Ali}
        \item Indirect detection of dark matter absorption in the Galactic Center \hfill \href{https://arxiv.org/abs/2404.17418}{arxiv}
        % \newline{\footnotesize \it Kimberly K. Boddy, Bhaskar Dutta, Addy J. Evans, \textbf{Wei-Chih Huang}, Stacie Moltner, Louis E. Strigari}
    \end{itemize}
\end{rSection}


\end{document}
