% https://www.overleaf.com/latex/templates/cis-grad-template-dev/pjcttwysqvym

% Use the custom resume.cls style
\documentclass{resume}

% Document margins
\usepackage[top=0.15in, bottom=0.15in, right=0.4in, left=0.3in]{geometry}
\usepackage{fontawesome}


\name{Wei-Chih Huang}
\address{
\href{mailto:noctildon2@gmail.com}{\faEnvelope\,noctildon2@gmail.com} \\
\href{https://www.linkedin.com/in/wei-chih-huang}{\faLinkedinSquare\,/in/wei-chih-huang} \\
\href{https://github.com/noctildon}{\faGithub\,noctildon} \\
\href{https://noctildon.github.io}{\faDesktop\,Personal Site} \\
\href{https://inspirehep.net/authors/2661451?ui-citation-summary=true}{\faGraduationCap\,Publications}
}

\begin{document}
% \vspace{-1em}
% \begin{rSection}{Objective}
%     Physics PhD candidate with extensive data analytical skills,
%     actively seeking opportunities in \textbf{\textit{data science/analysis}} within a vibrant and intellectually stimulating learning environment.
% \end{rSection}

\begin{rSection}{Education}
    {\bf PhD in Physics}, Texas A\&M University, US \hfill {Aug. 2019 - Dec. 2025} \\
    {\bf BS in Physics}, National Tsing Hua University, Taiwan \hfill {Aug. 2015 - Jun. 2019}
\end{rSection}



\begin{rSection}{Experience}
    \vspace{-1em}
    \item \textbf{Data scientist internship} - Capital One Auto Finance \hfill Jun. 2025 - Aug. 2025
        % \newline\hspace*{0.5em} {\normalsize}
        \begin{itemize}
        \item Reduced 10\% loss for auto loans with machine learning models (GBM, NN, LSTM) deployed on AWS
        \item Improved AUC by 10\% for future payments and default probability
        \item Designed customized PyTorch model, training loop and loss function to better align with business needs
        \item Built a scaleable data pipeline that fetched 10TB+ data from SnowFlake and processed analysis on AWS
        \item Collaborated with 4 product managers to translate model outputs into action-based decisions
        \end{itemize}

    \item \textbf{Machine learning engineer} - Firelight Innovations \hfill Aug. 2025 - Dec. 2025
        % \newline\hspace*{0.5em} {\normalsize}
        \begin{itemize}
        \item Engineered a cross-platform SDK (Python/TypeScript) to abstract BigQuery interactions, standardizing telemetry collection and simplifying data ingestion for internal teams.
        \item Deployed a scalable data lake architecture on GCS and BigQuery to drive visualization metrics for system health and user behavior
        \item Implemented PEFT pipelines for fine-tuning SLMs using Ollama and PyTorch, optimizing model inference for deployment on edge devices
        \end{itemize}

    \item \textbf{Quantitative Researcher/Engineer} - \href{https://www.linkedin.com/company/aggieqf}{Aggie Quant Fund} \hfill Jan. 2024 - Dec. 2024
        \newline\hspace*{0.5em} {\normalsize Application of cutting-edge technologies to financial market}
        \begin{itemize}
        \item Managed \$100,000 fund and developed models for stock forecasting and portfolio optimization
        \item Outperformed S\&P500 by 200\% by AI-driven strategies (sentiment analysis, LLMs, alpha research)
        \item Automated market insight extraction with LLM-powered pipelines, GitHub Actions, and Kubernetes
        \item Saved 70\% query time by high-performance market database (InfluxDB and PostgreSQL)
        \item Collaborated in a 10-person team to optimize portfolio, mitigate risks and monitor trades
        \end{itemize}

    \item \textbf{Research Assistant} - Physics Department, Texas A\&M University (\href{https://inspirehep.net/authors/2661451}{researcher profile}) \hfill Aug. 2019 - Jun. 2025
        \newline\hspace*{0.5em} {\normalsize PhD dissertation on high energy dark matter particle search}
        \begin{itemize}
        \item Published 7 papers in top journals and presented at international conferences
        \item Processed 1B+ rows of multi-dimensional data with Python/PySpark and accelerated analysis 1000× using C++, multiprocessing, and caching
        \item Orchestrated large-scale distributed data processing and HPC optimization using MPI/OpenMP and PySpark
        \item Reduced particle simulation runtime by 90\% with ML models (scikit-learn and PyTorch)
        \item Cut visualization runtime by 80\% using optimized NumPy/Pandas/Matplotlib workflows
        \item Built an interactive platform agnostic data dashboard using Streamlit and Docker
        \end{itemize}

    % \item \textbf{Full-Stack Web Developer/Project Manager} - \href{https://aggiecodingclub.com}{Aggie Coding Club} \hfill Jan. 2022 - Jan. 2023
    %     \newline\hspace*{0.5em} {\normalsize Dynamic website designed to cater to students' job-seeking requirements}
    %     \begin{itemize}
    %     \item Built a referral website to reduce the time of networking by 40\%
    %     \item Led a 10-member team to build and deploy a job referral web platform on GCP with Django/PostgreSQL
    %     \item Optimized schema design to reduce disk usage by 20\%, cutting hosting cost
    %     \end{itemize}

\end{rSection}


\begin{rSection}{SKILLS}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    ML/AI & PyTorch, scikit-learn, TensorFlow, NLP, Transformers\\
    MLOps/Infra & AWS, GCP, Snowflake, Linux, Docker, Kubernetes, Git, GitHub Actions, CI/CD\\
    Data/Database & NumPy, Pandas, SciPy, PySpark, InfluxDB, SQL, PostgreSQL\\
    Languages & Python, Bash, C/C\texttt{++}, SQL\\
    Visualization & Matplotlib, Seaborn, Streamlit
    \end{tabular}
\end{rSection}



% \vspace{0.5em}
% \begin{rSection}{Certifications}
%     \vspace{-1.2em}
%     \item ~~~~\textbullet~~Fundamentals of Accelerated Computing with CUDA C/C\texttt{++} \vspace{-0.5em}
%     \item \href{https://www.coursera.org/account/accomplishments/verify/N4T4JR8XLU3Z}{\color{black}{~~~~\textbullet~~Machine Learning Foundations: Algorithmic Foundations}} \vspace{-0.5em}
%     \item \href{https://www.coursera.org/account/accomplishments/verify/4X4TD24NFAY4}{\color{black}{~~~~\textbullet~~Machine Learning Foundations: Mathematical Foundations}} \vspace{-0.5em}
%     \item \href{https://www.coursera.org/account/accomplishments/verify/TJKKSPN42ZEE}{\color{black}{~~~~\textbullet~~Machine Learning Techniques}} \vspace{-0.5em}
%     \item \href{https://www.coursera.org/account/accomplishments/verify/KHCRSS4J4TZE}{\color{black}{~~~~\textbullet~~Divide and Conquer, Sorting and Searching, and Randomized Algorithms}} \vspace{-0.5em}
%     \item \href{https://www.coursera.org/account/accomplishments/verify/5B7WBDL9BHVF}{\color{black}{~~~~\textbullet~~A Crash Course in Causality: Inferring Causal Effects from Observational Data}}  \vspace{-0.5em}
% \end{rSection}




\end{document}
